---
title: "R Notebook"
output: html_notebook
---

This is a notebook to analyze and produce relevant plots about the analysis of the data from Ensemble Variation database.

```{r}
# Import librares
library(chromoMap)
library(tidyverse)
```

Import the data we extracted from the chromosome 1 VCF file with help of bcftools
```{r}
chromosome_data_path <- "/mnt/sda1/Databases/Ensembl/Variation/110/chromosomes_data/"
chromosome_n <- "chr3_data.tsv"
chromosome_n <- read_tsv(paste0(chromosome_data_path, chromosome_n))
names(chromosome_n)[1] <- "CHROM"
names(chromosome_n)[2] <- "POS"
names(chromosome_n)[3] <- "REF"
names(chromosome_n)[4] <- "ALT"
names(chromosome_n)[5] <- "TSA"
names(chromosome_n)[6] <- "ID"
```

Count the number of times a single locus is appears in the data
```{r}
counts <- chromosome_n %>% count(POS, sort = TRUE)
# Change the values of the CHROM column to make them compatible with chromoMap
counts$chrom <- "chr3"
counts$name <- "chr3_var"
names(counts)[1] <- "start"
names(counts)[2] <- "data"
counts$end <- counts$start
head(counts, 10)
```

Format the data for correct plotting with chromoMap:
```{r}
counts <- counts[, c('name','chrom','start','end','data')]
# Save for future use
output_path <- '/mnt/sda1/Databases/Ensembl/Variation/110/chromosomes_data/position_analysis/'
write_csv(counts, paste0(output_path,'chromosome3_repeated_positions.csv'))

# Filter those positions that appear 10 or more times
filtered_counts <- filter(counts, data >= 10)
head(filtered_counts)
write_csv(filtered_counts, paste0(output_path, 'filtered/chr2_filt_pos.csv'))
```


Plot the chromoMap example to look how the data has to be imputed
```{r}
chromosomes <- read.table("/home/moisessotelo/Documents/Universidad de Guadalajara/MBCI/Projecto/RuledDeepWAS/Scripts Preprocessing/chromosome_coordinates.txt", 
                          sep = "", header=TRUE) #add path
#annotation <- read.csv("./annotation.csv", header=TRUE) #add 


chromoMap(list(chromosomes), list(filtered_counts), data_based_color_map=T,
          data_type = 'numeric', plots = "bar")
```

# Create a vector of numbers from 1 to 10
numbers <- 1:10

# Use the paste function to create labels
label_list <- paste("label", numbers, sep = "_")

# Print the vector of labels
print(label_list)








